Reduced GW invariants from cuspidal curves

### 2018-01-09 draft_merged.tex
part. revised loc vir pb commutes with pf

We introduce two more spaces: let $\XP$ and $\Z^p$ be the algebraic stacks defined by the following cartesian diagram:
\bcd
\Z^p \ar[r,"\alpha"]\ar[d]\ar[rd,phantom,"\Box"] & \overline{\mathcal M}_1^{(1)}(\PP^4,d)^p \ar[d] \\
\XP \ar[r]\ar[d]\ar[rd,phantom,"\Box"] & \mathfrak{Pic}_1{(1)} \ar[d] \\
\X\ar[r] & \MM_1^{\rm{wt}}(1)
\ecd

@@

\subsection{Cosection Localized Virtual Pull-Back}
In this section we define an analogous of virtual pull-back \cite{Manolache} for localised cycles and we show that this operation commutes with proper push-forward. 
For the non expert reader, we first recall the basic construction of \cite{KLcosection}.
Let $Y\to S$ be a morphism of algebraic stacks of DM type and let $E$ over $Y$ be a vector bundle admitting a cosection

@@

surjective on an open $U$ and denote by $Y(\sigma)=Y\setminus E(\sigma).$ We use the following notation:

@@

 In the above setting we want to define a localized Gysin map

@@

 Let $B\in Z_*(E(\sigma)$ be a cycle represented by a closed integral sub-stack. If $B\subset  E\rvert_{Y(\sigma)}$ then
 \[s^!_{\sigma,\rm{loc}}[B]:=s^!_{E\rvert_{Y(\sigma)}}[B]\in A_*(Y(\sigma))\]
 and there is nothing to say as this is just the standard Gysin morphism.
 Suppose now $B$ is not contained in $E\rvert_{Y(\sigma)}.$ Then choose a variety $X\xrightarrow{\nu} Y$ such that:

@@

 \item The pull-back along $\nu$ of the cosection $\tilde{\sigma}=\nu^*\sigma$ give a surjective morphism

@@

 for $D$ a Cartier divisor in $X.$ Notice that the restriction of $\nu$ to the divisor give a proper morphism $D\xrightarrow{\nu(\sigma)} Y(\sigma);$
 \item there is a closed integral $\widetilde{B}\subset\widetilde{G}=\operatorname{Ker}(\tilde{\sigma})$ such that $\tilde{\nu}_*[\widetilde{B}]=k[B]$ for some $k\in\mathbb Z.$

@@

 We the define
 \[s^!_{\sigma,\rm{loc}}[B]:=k^{-1} \nu(\sigma)_*\left([D]\cdot s^!_{\widetilde{G}}[\widetilde{B}]\right)\,\in\,A_*(Y(\sigma)).\]
 In \cite[\S~2]{KLcosection} they prove that: such an $X$ always exist; the cycle $s^!_{\sigma,\rm{loc}}[B]$ is independent from the choice of $X;$ the construction preserves rational equivalences and thus define the wanted morphism.

@@

 If we consider as cycle in $E(\sigma)$ $[Y]$ thought as zero section of $E$, notice that a natural choice for $X$ is $\operatorname{Bl}_{Y(\sigma)}Y.$

@@

  Once defined such a operation, to get Theorem~1.1 in \cite{KLcosection} one would still need to show that: the same operation can be defined when we have a cosection of a vector bundle stacks $\mathbb E$ (easy to do if we have a surjection from a genuine vector bundle $E\to\mathbb E$, which is the situation in our case); the relative cone $\mathfrak C_{Y/S}\subseteq\mathbb{E}(\sigma),$ a sufficient condition for the latter to hold is that the cosection of the relative obstruction lifts to a cosection of the absolute obstruction \cite[Corollary~4.5]{KLcosecion}. 

@@

Let consider the cartesian diagram of algebraic stacks

@@

Y'\ar[r,"\varphi'"]\ar[d,"\rho'"] & Y\ar[d,"\rho"]\\

@@

lifting to a cosection of the absolute obstruction sheaf.
Then we can define a localised virtual cycle on $Y'$ supported on $Y'(\sigma')=Y(\sigma)\times_{Y} Y',$ where $\sigma'=\varphi'^*\sigma.$
Pulling back along $\varphi'$ endows $\rho'$ with a relative perfect obstruction theory $\mathbb E_{Y'/S'}:=\varphi'^*\mathbb E_{Y/S}.$ Furthermore, we can pull back the cosection 

@@

Notice that since $\sigma$ lifts to the absolute obstruction sheaf, $\sigma'$ does as well and it is plain that the degeneracy locus of $\sigma'$ is $Y'(\sigma')=Y(\sigma)\times_{Y} Y',$ which in turns implies that 
\[\varphi'^*\mathbb E_{Y/S}(\sigma)=\mathbb E_{Y'/S'}(\sigma').\]
Recall that, following the notation in \cite{KLcosection}, if $U\subseteq Y$ is the open where the cosection is surjective, we denoted
\[\mathbb E_{Y/S}(\sigma)=\mathbb E_{Y/S}\rvert_{Y(\sigma)}\cup\operatorname{Ker}\left(\mathbb E_{Y/S}\rvert_U \to \OO_Y\rvert_U\right).\]
By \cite[Corollary 5.4]{KLcosection} or by cartesianity of the diagram plus the discussion above,

@@

and we can thus define the localized virtual pull-back to be:
\[\varphi'^!_{\rm{loc}}[Y]^{\rm{vir}}_{\rm{loc}}=[Y']_{\rm{loc}}^{\rm{vir}}=s^!_{\sigma',\rm{loc}}[\mathfrak{C}_{Y'/S'}],\]
compare also with \cite[Theorem~5.2]{KLcosection}

The above construction applies to $\Z^p$.
Indeed, consider on $\Z^p$ the perfect obstruction theory $\mathbb E_{\Z^p/\XP}:=\alpha^*\left(\mathbb E_{\Mone{1}{\PP^4}{d}^p/\mathfrak{Pic_1{(1)}}}\right)$ and the induces cosection
\[\alpha^*\sigma\colon \OO b_{\Z^p/\XP}\to \Z^p\]
whose degeneracy locus is
\[\pazocal D(\alpha^*\sigma)=\pazocal D(\sigma)\times_{\Mone{1}{\PP^4}{d}^p} \Z^p.\]
Then we have that
\begin{align*}
\mathfrak C_{\Z^p/\XP}& \subseteq \alpha^*\mathfrak C_{\Mone{1}{\PP^4}{d}^p/\mathfrak{Pic_1{(1)}}}\\
& \subseteq \alpha^* h^1/h^0\left(\mathbb E_{\Mone{1}{\PP^4}{d}^p/\mathfrak{Pic_1{(1)}}}\right)_\sigma\\
&\cong h^1/h^0\left(\mathbb E_{\Z^p/\XP}\right)_{\alpha^*\sigma}
\end{align*}
and we can thus define $[\Z^p]^{\rm{vir}}_{\alpha^*\sigma,\rm{loc}}.$
\begin{lem}\label{lem:comutativity}
In the setting of the localised virtual-pullback definition, suppose furthermore that $\varphi$ is proper and $\varphi'(Y')\cap U\neq\emptyset$ then
for any $[B']\in A_*(\varphi'^*\mathbb{E}(\sigma'))$
\begin{equation}\label{eq:commcos}\varphi'_*( s^!_{\sigma',\rm{loc}}[B'])=s^!_{\sigma,\rm{loc}}\left(\varphi^{\mathbb{E}}_*[B']\right)\,\in\, A_*(Y(\sigma)) 
\end{equation}
where $\varphi^{\mathbb{E}}\colon \varphi'^*\mathbb{E}(\sigma')\to \mathbb{E}(\sigma)$ is the natural induced morphism.
\end{lem}
\begin{proof}
If $B'\subset \mathbb{E}\rvert_{Y'(\sigma')}$ then $\varphi(\sigma)(B')\subset \mathbb{E}\rvert_{Y(\sigma)}$
thus the localised Gysin morphism are just $s^!_{\mathbb{E}\rvert_{Y'(\sigma')}}$, $s^!_{\mathbb{E}\rvert_{Y(\sigma)}}$ and the fact they commute with proper push-forward is already well known, see \cite{Kresh} or simply \cite[Chapter~4]{Fulton} if we assume the existence of global resolutions.

>>>>

We introduce two more spaces: let $\XP$ and $\Z^p$ be the algebraic stacks defined by the following cartesian diagram:
\bcd
\Z^p \ar[r,"\alpha"]\ar[d,"\gamma"]\ar[rd,phantom,"\Box"] & \overline{\mathcal M}_1^{(1)}(\PP^4,d)^p \ar[d] \\
\XP \ar[r]\ar[d]\ar[rd,phantom,"\Box"] & \mathfrak{Pic}_1{(1)} \ar[d] \\
\X\ar[r] & \MM_1^{\rm{wt}}(1)
\ecd

@@

\subsection{Cosection-localised virtual pullback}
In this section we slightly generalise the notion of virtual pullback \cite{Manolache-pullback} to localised cycles and we show that this operation commutes with proper pushforward. 
We start by recalling the construction of \cite{KLcosection} for the benefit of the non-expert reader.

Let $Y\to S$ be a morphism of algebraic stacks of DM type and let $E$ be a vector bundle over $Y$ admitting a cosection

@@

surjective on an open $U\subseteq Y$; denote by $Y(\sigma)$ the complement $Y\setminus U.$ Recall the following notation from \cite{KLcosection}:

@@

 Kiem and Li define a localized Gysin map:

@@

 Let $[B]\in Z_*(E(\sigma))$ be a cycle represented by a closed integral substack. If $B\subset  E\rvert_{Y(\sigma)}$ then
  they just consider the standard Gysin morphism: \[s^!_{\sigma,\rm{loc}}[B]:=s^!_{E\rvert_{Y(\sigma)}}[B]\in A_*(Y(\sigma)).\]
 Suppose now that $B$ is not contained in $E\rvert_{Y(\sigma)}.$ Then we may choose a variety $X\xrightarrow{\nu} Y$ such that:

@@

 \item the pullback along $\nu$ of the cosection $\nu^*\sigma=:\tilde{\sigma}$ extends to a surjective morphism

@@

 for a Cartier divisor $D\subseteq X.$ The restriction of $\nu$ to the divisor gives a proper morphism $\nu(\sigma)\colon D\to Y(\sigma);$
 \item there is a closed integral $\widetilde{B}\subset\widetilde{G}=\operatorname{Ker}(\tilde{\sigma})$ such that $\tilde{\nu}_*[\widetilde{B}]=k[B]$ for some $k\in\mathbb N.$

@@

 The localised Gysin pullback is then defined as:
 \[s^!_{\sigma,\rm{loc}}[B]:=\frac{1}{k} \nu(\sigma)_*\left([D]\cdot s^!_{\widetilde{G}}[\widetilde{B}]\right)\,\in\,A_*(Y(\sigma)).\]
 In \cite[\S~2]{KLcosection} they prove that: such $(X,\nu,\widetilde B)$ always exist; the cycle $s^!_{\sigma,\rm{loc}}[B]$ is independent of the above choices; the construction preserves rational equivalences and thus defines the desired morphism on Chow groups.

@@

 If we consider $[Y]$ as a cycle in $E(\sigma)$, thought of as the zero section of $E$, notice that a natural choice for $X$ is $\operatorname{Bl}_{Y(\sigma)}Y.$

@@

  Kiem and Li then proceed to extend the cosection-localised Gysin pullback to vector bundle stacks $h^1/h^0(\mathbb E)$ (this is relatively easy in the presence of a global resolution, which is the case in the situation at hand); they show that the intrinsic normal cone $\mathfrak C_{Y/S}$ is contained in the closed substack $h^1/h^0(\mathbb{E})(\sigma),$ at least when the cosection of the relative obstruction bundle lifts to a cosection of the absolute obstruction bundle \cite[Corollary~4.5]{KLcosection}. 

@@

Consider a cartesian diagram of stacks:

@@

Y'\ar[r,"\varphi'"]\ar[d,"\rho'"]\ar[dr,phantom,"\Box"] & Y\ar[d,"\rho"]\\

@@

that lifts to a cosection of the absolute obstruction sheaf $\OO b_Y$.
Then we can define a localised virtual pullback operation: \[(\rho')^!_{\mathbb E_{Y'/S'},\sigma'}\colon A_*(S')\to A_{*-\operatorname{rk}(\mathbb E)}(Y'(\sigma'))\] where $\sigma'=(\varphi')^*(\sigma)$ and $Y'(\sigma')=Y(\sigma)\times_{Y} Y'$.
Replace $S'$ by a primitive cycle in it, i.e. assume that $S'$ is irreducible and reduced. Recall that pulling back $\mathbb E_{Y/S}$ along $\varphi'$ endows $\rho'$ with a relative perfect obstruction theory $\mathbb E_{Y'/S'}:=(\varphi')^*\mathbb E_{Y/S}.$ Furthermore notice that we can pullback the cosection:

@@

Notice that since $\sigma$ lifts to the absolute obstruction sheaf, $\sigma'$ does as well. The degeneracy locus of $\sigma'$ is $Y'(\sigma')=Y(\sigma)\times_{Y} Y',$ which in turns implies that:
\[h^1/h^0(\mathbb E_{Y'/S'})(\sigma')=(\varphi')^*h^1/h^0(\mathbb E_{Y/S})(\sigma).\]
%Recall that, following the notation in \cite{KLcosection}, if $U\subseteq Y$ is the open where the cosection is surjective, we denoted
%\[\mathbb E_{Y/S}(\sigma)=\mathbb E_{Y/S}\rvert_{Y(\sigma)}\cup\operatorname{Ker}\left(\mathbb E_{Y/S}\rvert_U \to \OO_Y\rvert_U\right).\]
By \cite[Corollary 4.5]{KLcosection} and by the cartesian diagram above,

@@

thus we can define the localised virtual pullback of $[S']$ to be:
\[(\rho')^!_{\mathbb E_{Y'/S'},\sigma'}[S']=s^!_{\sigma',\rm{loc}}[\mathfrak{C}_{Y'/S'}].\]
%compare also with \cite[Theorem~5.2]{KLcosection}

The above construction applies to $\Z^p$.
Indeed consider on $\Z^p$ the perfect obstruction theory: \[\mathbb E_{\Z^p/\XP}:=\alpha^*\left(\mathbb E_{\Mone{1}{\PP^4}{d}^p/\mathfrak{Pic}_1{(1)}}\right)\] and the induced cosection
$\alpha^*\sigma\colon \OO b_{\Z^p/\XP}\to \Z^p$
with degeneracy locus:
\[\pazocal D(\alpha^*\sigma)=\Mone{1}{X}{d}\times_{\Mone{1}{\PP^4}{d}^p} \Z^p.\]
Then we have that
\begin{align*}
\mathfrak C_{\Z^p/\XP}& \subseteq \alpha^*\mathfrak C_{\Mone{1}{\PP^4}{d}^p/\mathfrak{Pic_1}{(1)}}\\
& \subseteq \alpha^* h^1/h^0\left(\mathbb E_{\Mone{1}{\PP^4}{d}^p/\mathfrak{Pic_1{(1)}}}\right)(\sigma)\\
&\cong h^1/h^0\left(\mathbb E_{\Z^p/\XP}\right)(\alpha^*\sigma)
\end{align*}
and we can thus define $[\Z^p]^{\rm{vir}}_{\alpha^*\sigma,\rm{loc}}:=\gamma^!_{\mathbb E_{\Z^p/\XP},\alpha^*\sigma}[\XP].$
\begin{lem}\label{lem:comutativity}
With the same setup and notation as in the definition of localised virtual pullback, suppose furthermore that $\varphi$ is proper and $\varphi'(Y')\cap U\neq\emptyset$. then
for any $[B']\in A_*(\varphi'^*\mathbb{E}(\sigma'))$
\begin{equation}\label{eq:commcos}\varphi'_*( s^!_{\sigma',\rm{loc}}[B'])=s^!_{\sigma,\rm{loc}}\left(\varphi^{\mathbb{E}}_*[B']\right)\,\in\, A_*(Y(\sigma)) 
\end{equation}
where $\varphi^{\mathbb{E}}\colon \varphi'^*\mathbb{E}(\sigma')\to \mathbb{E}(\sigma)$ is the natural induced morphism.
\end{lem}
\begin{proof}
If $B'\subset \mathbb{E}\rvert_{Y'(\sigma')}$ then $\varphi(\sigma)(B')\subset \mathbb{E}\rvert_{Y(\sigma)}$
thus the localised Gysin morphism are just $s^!_{\mathbb{E}\rvert_{Y'(\sigma')}}$, $s^!_{\mathbb{E}\rvert_{Y(\sigma)}}$ and the fact they commute with proper push-forward is already well known, see \cite{Kresh} or simply \cite[Chapter~4]{Fulton} if we assume the existence of global resolutions.
